High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 conclusion.tex
ORNL acknowledgment.

{\bf \footnotesize This work is funded by DOE XXXXXX \par}

>>>>

{\bf \footnotesize Acknowledgements: This work is funded by DOE XXXXXX This
research used resources of the Oak Ridge Leadership Computing Facility at the
Oak Ridge National Laboratory, which is supported by the Office of Science of
the U.S.Department of Energy under Contract No. DE-AC05-00OR22725. \par}
